Notes on Wide Gap

### 2016-02-27 paper/wide_gap_notes.tex
susan question on definition of streamfunction
susan question about streamfunction answered
B_phi term confirmed correct
got something different for vector potential eqn... will check
susan still gets different terms for A equation.... please check?
fixed typos in u_phi equation. I think this matches Susan's now...
Fixed A equation: Susan was right. I was using a different (and wrong!) definition of B from A.
r component of Psi equation in expanded form
z component of Psi equation in expanded form
missing term
typo
never mind the recent commits they are wrong
detailed derivation of Psi equatio

\section{Basic Equations}
\label{sec:equations}
The so-called Stokes stream function, used in axisymmetric situations, is given by 
\begin{equation}
  \label{eq:stokes}
  \mathbf{u} \, = \, \left[\begin{matrix}
\frac{1}{r} \partial_z \psi\ \rhat\\
\uphi \ \phihat\\
-\frac{1}{r} \partial_r \psi\ \zhat\\
\end{matrix}\right];
\end{equation}
here we define $A$ in the same way.

@@

\begin{equation}
  \label{eq:uy}
\partial_t \uphi + J(\psi, \uphi) + \frac{\uphi \partial_r \psi}{r^2} = J(B_\phi, A) - \frac{B_\phi \partial_z A}{r^2} + \nu \left( \nabla^2 \uphi - \frac{\uphi}{r}\right)
\end{equation}

\begin{equation}
  \label{eq:A}
\partial_t A = \frac{1}{r^2} J(\psi, A) - \eta \left[ \frac{1}{r}\left( \nabla^2 A - \frac{2 \partial_r A}{r} \right)\right]
\end{equation}

\begin{multline}
  \label{eq:By}
\partial_t B_\phi = \frac{1}{r} J(A, \uphi) + \frac{1}{r} J(B_\phi, \psi)\\
+ \frac{1}{r^2} B_\phi \partial_z \psi - \frac{1}{r^2} \uphi \partial_z A + \eta \left(\nabla^2 B_\phi - \frac{1}{r^2} B_\phi \right)
\end{multline}

@@

\begin{equation}
  \label{eq:vec_lap_z}
  (\nabla^2 \mathbf{u})_z = \nabla^2 u_z,
\end{equation}
where $\nabla$ on the vector components is given by equation~(\ref{eq:del_scalar}).
\end{document}

>>>>

\section{Basic Equations}
\label{sec:equations}
The so-called Stokes stream function, used in axisymmetric situations, is given by 
\begin{equation}
  \label{eq:stokes}
  \mathbf{u} \, = \, \left[\begin{matrix}
\frac{1}{r} \partial_z \psi\ \rhat\\
\uphi \ \phihat\\
-\frac{1}{r} \partial_r \psi\ \zhat\\
\end{matrix}\right];
\end{equation}
here we define $A$ in the same way. \\

@@

For the expanded form of the $\Psi$ equation, Susan gets:

\begin{equation}
  \label{eq:uy}
\partial_t \uphi + \frac{J(\psi, \uphi)}{r} + \frac{\uphi \partial_z \psi}{r^2} = \frac{J(A, B_\phi)}{r} + \frac{B_\phi \partial_z A}{r^2} + \nu \left( \nabla^2 \uphi - \frac{\uphi}{r}\right)
\end{equation}

\begin{equation}
  \label{eq:A}
\partial_t A = \frac{1}{r} J(A, \psi) + \eta \left( \nabla^2 A - \frac{2 \partial_r A}{r} \right)
\end{equation}

Susan gets:
\beq
\partial_t A = \frac{1}{r} J(A, \Psi) + \frac{1}{Rm} \left[ -\frac{1}{r} \partial_r A + \partial_r^2 A + \partial_z^2 A\right]
\eeq
%Susan got:
%beq
%\partial_t A = \frac{2}{r} J(A, \Psi) + \frac{1}{Rm} \left[ \nabla^2 A - \frac{2}{r} \partial_r A \right]
%\eeq
%....will check.

\begin{multline}
  \label{eq:By} % Susan confirms correct 1/14/16
\partial_t B_\phi = \frac{1}{r} J(A, \uphi) + \frac{1}{r} J(B_\phi, \psi)\\
+ \frac{1}{r^2} B_\phi \partial_z \psi - \frac{1}{r^2} \uphi \partial_z A + \eta \left(\nabla^2 B_\phi - \frac{1}{r^2} B_\phi \right)
\end{multline}

\section{Detailed Derivation of $\Psi$ Equation}
The $\Psi$ equation, governing the x- and z-components of the velocity, is particularly tricky to derive so I will write out the steps here.

1. Find x and z components of the momentum equation, i.e.:

\beq
\partial_t u_z + \left[u \cdot \nabla u \right]_z = \left[ \left( \nabla \times B \right) \times B \right]_z + \frac{1}{\reye}\left[ \nabla^2 u \right] _z
\eeq

Which becomes

\beq
\frac{1}{r^2} \partial_t \partial_r \Psi
\eeq

@@

\begin{equation}
  \label{eq:vec_lap_z}
  (\nabla^2 \mathbf{u})_z = \nabla^2 u_z,
\end{equation}
where $\nabla$ on the vector components is given by equation~(\ref{eq:del_scalar}).

Note that, expanding the definition of the vector Laplacian, where the cylindrical scalar Laplacian is substituted in for $\nabla^2 u_r$ and $\nabla^2 u_z$

\end{document}
